---
output: github_document
---


# movebank


## Installing:

## Use

```{r message=FALSE}
library("movebank")
library("tidyverse")
library("sf")
```

```{r}
readRenviron(".Renviron")
```


For some endpoints we can successfully get the full table in a single call:

```{r message = FALSE}
study <- movebank("study") ## temporal & geographic coverage, but no species coverage information
taxon <- movebank("taxon") ## Purely a taxonomic database, has no connection to study
tag_type <- movebank("tag_type") ## small table listing information the different types of animal tracker tags
```


```{r}
study$i_can_see_data %>% as.logical() %>% sum()
```

```{r}
study$there_are_data_which_i_cannot_see %>% as.logical() %>% sum()
```

That seems terribly optimistic.  For instance, 

```{r}
study[1,]$there_are_data_which_i_cannot_see
```

claims there are data for this study, even though the online search tool says there are not.  

Even studies that do show up when I check the "Only studies where I can see data" option in the online tool often seem to tell me that "there is no data available to download" (e.g. study titled "a week in the life of a pygmy blue whale").

Other studies (e.g. the study titled "(EBD) Lesser Kestrels") does let me download the data after accepting an agreement.  

```{r}
study %>% filter(grepl("Lesser Kestrels", name)) %>% select(id, name, i_can_see_data, there_are_data_which_i_cannot_see)
```

- How do I request ESRI format for data download?  (online tool gives this option)


```{r}
public <- study %>% filter(i_can_see_data == "true") %>% pull(id)
```

Let's see if we can get data from any of the `individual` tables. We'll try every study:

```{r message=FALSE}
individual <- map(public, safely(function(i) movebank("individual", study_id = i)))
tag <- map(public, safely(function(i) movebank("tag", study_id = i)))
event <- map(public, safely(function(i) movebank("event", study_id = i)))

## cases where we can see data
sum(!sapply(individual, is.character))
```






-----------

Getting the actual data requires we accept the license terms first.

Data tables for individual, tag, and event require a study-id to avoid a 500-error.

```{r}
movebank("individual", study_id=study$id[[1]])
movebank("tag", study_id=study$id[[1]])
movebank("event", study_id=study$id[[1]])
```



```{r}
sensor <- movebank("sensor", external_id=tag_type$external_id[[1]])
```


Connect taxonomic information to study data:  Taxonomic information can only be found in the "individual" table (which fortunately also has a key to `study_id`).  

Unfortunately, most data in the `individual` table cannot be accepted 

----

Example: use `ritis` to search for all matches to a given higher-level taxonomic group, e.g. all birds, all reptiles.

Example: Look up scientific name, or add common names to data.

```{r message=FALSE}
#library(ritis)
```

```{r}
tag_ex <- movebank("tag", study_id=2911040)
event_ex <- movebank("event", study_id=2911040)
```

```{r}
df %>%
  select(id,
         principal_investigator_name,
         study_type,
         study_objective,
         timestamp_start,
         timestamp_end,
         bounding_box)
```

