---
output: github_document
---


# movebank


## Installing:

## Use

```{r message=FALSE}
library("movebank")
library("tidyverse")
library("sf")
```

```{r}
readRenviron(".Renviron")
```


For some endpoints we can successfully get the full table in a single call:

```{r message = FALSE}
study <- movebank("study") ## temporal & geographic coverage, but no species coverage information
taxon <- movebank("taxon") ## Purely a taxonomic database, has no connection to study
tag_type <- movebank("tag_type") ## small table listing information the different types of animal tracker tags
```


```{r}
study$i_can_see_data %>% as.logical() %>% sum()
```

```{r}
study$there_are_data_which_i_cannot_see %>% as.logical() %>% sum()
```

That seems terribly optimistic.  For instance, 

```{r}
study[1,]$there_are_data_which_i_cannot_see
```

claims there are data for this study, even though the online search tool says there are not.  

Even studies that do show up when I check the "Only studies where I can see data" option in the online tool often seem to tell me that "there is no data available to download" (e.g. study titled "a week in the life of a pygmy blue whale").

Other studies (e.g. the study titled "(EBD) Lesser Kestrels") does let me download the data after accepting an agreement.  

```{r}
study %>% filter(grepl("Lesser Kestrels", name)) %>% select(id, name, i_can_see_data, there_are_data_which_i_cannot_see)
```

- How do I request ESRI format for data download?  (online tool gives this option)


```{r}
public <- study %>% filter(i_can_see_data == "true") %>% pull(id)
```

Let's see if we can get data from any of the `individual` tables. We'll try every public study:

```{r message=FALSE}
individual <- map(public, safely(function(i) movebank("individual", study_id = i)))
tag <- map(public, safely(function(i) movebank("tag", study_id = i))) 
event <- map(public, safely(function(i) movebank("event", study_id = i)))

## not so much
individual <- map(individual, "result")
sum(sapply(individual, is.data.frame))


tag <- map(tag, "result")
sum(sapply(tag, is.data.frame))
event <- map(event, "result")
sum(sapply(event, is.data.frame))

who <- sapply(event, is.data.frame)
who2 <- sapply(tag, is.data.frame)
identical(who, who2) ## same 46 with data?

## just the data please
id <- public[who] # the actually public data
individual <- individual[who]
tag <- tag[who]
event <- event[who]
```






-----------

Getting the actual data requires we accept the license terms first.
Connect taxonomic information to study data:  Taxonomic information can only be found in the "individual" table (which fortunately also has a key to `study_id`).  



----

Example: use `ritis` to search for all matches to a given higher-level taxonomic group, e.g. all birds, all reptiles.

Example: Look up scientific name, or add common names to data.

```{r message=FALSE}
#library(ritis)
```

```{r}
tag_ex <- movebank("tag", study_id=2911040)
event_ex <- movebank("event", study_id=2911040)
```

```{r}
df %>%
  select(id,
         principal_investigator_name,
         study_type,
         study_objective,
         timestamp_start,
         timestamp_end,
         bounding_box)
```

# move package comparison

testing move commands:

```{r}
library("move")
login <- movebankLogin(username=Sys.getenv("MOVEBANK_USER"), password=Sys.getenv("MOVEBANK_PW"))

## the tag_type table
sensors <- getMovebankSensors(login=login)

ex_sensorAttr <- getMovebankSensorsAttributes("BCI Ocelot",login=login)
ex_individuals <- getMovebankAnimals(study="BCI Ocelot",login=login)
indiv_path <- getMovebankData(study="BCI Ocelot", animalName="Bobby", login=login)

## study id for BCI Ocelot. (methods can use id, recognized by int signature)
ocelot <- 123413
ex_sensorAttr <- getMovebankSensorsAttributes(ocelot,login=login)
```

```{r}
study_table <- getMovebank("study", login=login)
```


`move` seems to have forgotten the filter, or seems to think that requesting attribute column is the same thing as requesting where that attribute column evaluates to "true"?  Note there is no way here to get the rest of the study info.  

```{r}
showMethods("getMovebankStudies", includeDefs = TRUE)
```

